\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[pdftex]{graphicx}
\graphicspath{{./fig/}}

\title{Topic Modeling Library and Framework User Guide}
\author{Avanesov Valeriy\\Kozlov Ilya}
\date{\today}

\usepackage{natbib}
\usepackage{hyperref}
\begin{document}

\maketitle

\section{Input}
    The aim of this project is to provide flexible and simple library and framework for topic modeling.
    The main properties of this project:
    \begin{itemize}
	\item Ability to apply user-defined regularizer, sparsifier and stopping criteria.
	\item Ability to use multilingual topic modeling. 
    \end{itemize}
    The paper is organized as follow: section \ref{intro} contains a quick introduction to topic modeling,
    \ref{quickStart} describes how to start a project without description of details of implementation. These two sections should allow you
    to use LDA and PLSA  model in simple use\--cases. The following section describes details of implementation and is necessary for
    deeper understanding of project structure and implementation of your own regularizer, sparsifier and other stuff.
    Section \ref{projectStructure} describes a structure of the project, section \ref{regularizer} describes regularizers and explains how to implement your
    own regularizer, section \ref{sparsifier} describes what sparsifier is and how to implement you own sparsifier. Section \ref{stoppingCriteria} for the 
    description of how to define that convergence of EM-algorithm is achieved. Section \ref{multilingual} describes (actually, it doesn't, though we are working on it) how to use model in multilingual setting. 

\clearpage	\section{Introduction to topic modeling}  \label{intro} \input{intro.tex}

\clearpage	\section{Quick start} \label{quickStart} \input{quickStart.tex}

\clearpage	\section{Building bricks of our model} \label{projectStructure} \input{buildingbrics.tex}

\clearpage	\section{Regularizer} \label{regularizer} \input{regularizer.tex}

\clearpage	\section{Sparsifier} \label{sparsifier} \input{sparsifier.tex}

\clearpage	\section{Stopping Criteria} \label{stoppingCriteria} \input{stoppingCriteria.tex}

\clearpage	\section{Multilingual topic modeling} \label{multilingual}

\bibliographystyle{unsrt}
\bibliography{userGuide} 
\end{document}
